On $k$-tactics in Gruenhage's compact-point game

### 2015-03-25 articles/k-tactics-in-gruenhages-compact-point-game/article.tex
add acknowledgements and other small tweaks

This question is very similar to the open question on the well-known
Banach-Mazur (also known as Choquet) game $\bmGame{X}$ where $\pl N$
is the player wishing for a nonempty intersection: does there exist a
space for which
$\pl N\ktactwin{3}\bmGame{X}$ but $\pl N\notktactwin{2}\bmGame{X}$?
(The analogous question for $2$- and $1$-tactics was answered in the
affirmative by Gabriel Debs in \cite{MR817083}.) For fans
of such infinite combinatorial game theory puzzles, we may restate the
main question as follows.

@@

>>>>

This question is very similar to the open question on the well-known
Banach-Mazur (a.k.a. Choquet) game $\bmGame{X}$: does there exist a
space for which
$\pl N\ktactwin{3}\bmGame{X}$ but $\pl N\notktactwin{2}\bmGame{X}$
(where $\pl N$
is the player wishing for a nonempty intersection)?\footnote{
  The analogous question for $2$- and $1$-tactics was answered in the
  affirmative by Gabriel Debs in \cite{MR817083}.
}
For fans
of such infinite combinatorial game theory puzzles, we may restate the
main question as follows.

@@

\section{Acknowledgements}

The author would like to thank his PhD advisor Gary Gruenhage for his
support and mentorship while the author developed these results as a part of
his dissertation.
